\section*{EXPERIENCE}

\noindent
\textbf{\href{https://yandex.com}{Yandex}} \hfill Russia, Moscow\\ 
\textit{Intern Machine Learning Engineer} \hfill June 2023 - September 2023 
\begin{itemize}
\item Successfully researched how to finetune model in order to apply quantization, before model was trained with LoRa and could not be quantized. The quality increased by SbS, GPU memory consumption and inference time reduced twice. You can try the summarization model \href{https://300.ya.ru}{here}.
\item Completely on my own implemented chats summarization model, I was responsible for all steps of the chat summarization process, from collecting data in real-time and training model to building a service that responds to summarization requests.
\item Invented and implemented quality metrics for the summarization task, which simplified choosing the best model.
\item Added reward models and researched its' quality for the summarization task according to team's and assessors' markups. As the result, it dramatically simplified and accelerated experiments and models comparison.
\item Participated in the new YandexGPT model launch.  
\item Fixed and improved team's training, testing pipelines. Added reward model metrics into the training and production pipelines. 
\item Implemented pipeline for automatic searching optimal inference configuration and found better inference config.
\item Invented and implemented production-ready algorithm based on DSSM-model for linking a summary thesis to the certain position in the text, it achieved 99\% accuracy. Advised backend team in the algorithm implementation.
\item Noticed ineffective markup method and proved why it prevented to use better model in the production. As a result, choosing the best model approach was changed to SbS markup. Also proposed bayesian estimation for more detailed assessors' markup analysis.
\item Entirely created questions \& answers knowledge base (approximitely 500k QAs) for a new Yandex QA-service.
\item Invented and implemented answers fact checking algorithm. It had high correlation between assessors' markup and answers' correctness, thus all answers could be qualified as accurate or uncertain. It created new useful functionality for the service and led to substantial cost reduction and process simplification.
\item Completely on my own implemented and supported an internal telegram bot for scheduled summarization in yandex business chats.
\end{itemize}

\noindent
\textbf{Mosaic Capital} \hfill Australia, remote\\ % Company name and location
\textit{Intern Researcher} \hfill July 2022 - September 2022 % Position and duration
\begin{itemize}
\item Implemented log-parser for collecting and calculating features.
\item Implemented model predicting future price in 1-3 minutes.
\item Implemented, trained and compared different ML-models for predicting price. Best result for predicting price in 1 minute with LSTM-model is R2=0.37.
\end{itemize}

\noindent
\textbf{AIMTech (currently, \href{https://pinely.com}{Pinely})} \hfill Moscow, Russia\\ 
\textit{Intern Researcher} \hfill August 2021 -- October 2021 % Position and duration
\begin{itemize}
\item Invented and implemented order position tracking algorithm and covered it by unit tests. Invented and implemented 2 metrics for verifying my algorithm quality. My order queue tracking was close to alternative queue tracking, which implementation was slow. Team  and I used prediction for improving strategy performance in production.
\item Invented and implemented orders cancelling method, which could delete unprofitable orders. It made the strategy less risky and more profitable, 15\% increase in daily profit in the simulator.
\item Noticed non-optimal implementation in the most important part of the code (hot way). Proposed and implemented faster solution.
\item Noticed and fixed bug in the team's strategy code, which could affect production result.
\item Noticed critical error in team's member analysis, which had been stopping research progress for 3 weeks. 
\item Implemented utilities in C++: orders profit estimator, basic classes for incoming and outgoing objects, etc.
\item Implemented utilities in Python: measuring and comparing code latency, cancelled orders analysis.
\end{itemize}

\noindent
\textbf{\href{https://www.tinkoff.ru}{Tinkoff Bank}} \hfill Moscow, Russia \\ 
\textit{Intern Analyst} \hfill April 2021 -- July 2021
\begin{itemize}
\item Implemented several profitable trading strategies, implemented several models for predicting stock price.
\item Fully on my own implemented exchange simulator in Python, which simulated the whole trading process.
\end{itemize} 

% Club or Organization Experience
\textbf{Other experience} \hfill \\
\textit{Machine Learning Teaching Assistant at the HSE} \hfill January 2024 -- June 2024\\ 
\textit{Matrix Computation Teaching Assistant at the HSE} \hfill January 2023 -- June 2023\\ 
\textit{Mathematical Statistics Teaching Assistant at the HSE} \hfill January 2023 -- June 2023\\ 
\textit{Python Teaching Assistant at the HSE} \hfill September 2022 -- December 2022\\
\textit{Algorithms and Data Structures Teacher for high school students} \hfill September 2020 -- December 2021\\